Predicted cardiovascular risk for adults in the US with diabetes, chronic kidney disease, and ≥ 65 years of age

### 2021-03-24 docs/index.Rmd
getting slides online

@@

>>>>

Blood and urine samples were collected during the medical examination. Serum creatinine, serum glucose and glycated hemoglobin were measured using standard methods.

Estimated glomerular filtration rate was calculated using the CKD Epidemiology Collaboration equation. Urinary albumin and creatinine levels were measured and used to calculate the albumin-to-creatinine ratio.

- Diabetes was defined by fasting plasma glucose ≥ <span style="color:purple"><b>`r gluc_cutpoint_fasted`</b></span> mg/dL (≥ <span style="color:purple"><b>`r gluc_cutpoint_fed`</b></span> mg/dL for those who were not fasting), glycated hemoglobin ≥ <span style="color:purple"><b>`r hba1c_cutpoint`</b></span>%, or self-reported use of insulin or oral glucose lowering medication

- CKD was defined by an estimated glomerular filtration rate < <span style="color:purple"><b>`r egfr_cutpoint`</b></span> ml/min/1.73m<sup>2</sup> or an albumin-to-creatinine ratio ≥ <span style="color:purple"><b>`r acr_cutpoint`</b></span> mg/g.

@@

# Demo
